Approximation as Differentiation

### 2025-07-10 main/conclusion.tex
Some blurb on source transformation approach.

Would be better to have an implementation that worked by translation,
instead of interpreting directly as Agda functions. See work by
Smeding and Vákár on translations. To formalise this, we'd need
to... See also $\Fam(\PSh_{\CMon}(\namedcat{Syn}))$?

>>>>

% To formalise this, we'd need to... See also $\Fam(\PSh_{\CMon}(\namedcat{Syn}))$?

An interesting implementation technique, as an alternative the denotational approach presented here or the
trace-based approaches used in earlier \GPS implementations, would be to develop a source-to-source
transformation, in direct analogy with the CHAD approach to automatic differentiation
\cite{vakar22,nunes2023}. In their approach, forward and reverse-mode AD are implemented as compositional
transformations on source code, guided by a universal property: they arise as the unique structure-preserving
functors from the source language to a suitably structured target language formalised as a Grothendieck
construction. Adapting this to Galois slicing would allow slicing to ``compiled in'', avoiding the need for a
custom interpreter and presenting opportunities for optimisation.
